Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-27 paper.tex
add latency explanation

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/mmap_latency}
    \caption{Latency of memory operations}
\end{figure}

>>>>

Figure \ref{fig:mmap_latency} shows for various microbenchmarks the time taken per mmap operation 
as it varies with the total amount memory allocate so far in the system. As described above, we use 
rdtsc to find the number of ticks taken for the operation and then calibrate rdtsc to conver
these ticks into microseconds. It can be seen that for continuous mmaps the time is not only the lowest
but also invariant with the total number of mmaps done so far. This is because of two reasons. First, 
when a continuous mmap (with the same permissions) happens the kernel memory allocator does not need 
create a new vm area struct, instead it modifies the adjacent vm area structs to account for the newly 
accommodate memory. This ensures that there is no need to perform the lookup on the red black trees that 
store the vm area sturct so a constant line is seen.

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/mmap_latency}
    \caption{Latency of memory operations}
    \label{fig:mmap_latency}
\end{figure}
